Using reference models in variable selection \vspace{.1in}

### 2020-02-04 paper/ref_approach.tex
minor edits about iterative lasso

@@

Figure \ref{fig:sensitivity_vs_fdr_iterated} shows the average sensitivity on
the vertical axis and the average false discovery rate on the
horizontal axis based on 100 data simulations for the different
combinations of $n$ and $\rho$. The best selection performance is on the
top-left corner of each plot, as it implies the lowest false discovery
rate and the highest sensitivity. We see that regardless of the
applied selection method, the use of a reference model improves the
selection performance, as it reduces the false discovery rate (shifting
to the left) or increases the sensitivity (shifting upwards). In
accordance with what can be expected, the larger data set size ($n$) and the higher the true correlations ($\rho$), the easier the
selection is. Thus, for easier selection scenarios, the benefits of
the reference model are smaller since the raw data already provide
enough information to identify the relevant variables. The iterative
projpred has good false discovery rate in all cases, and the
sensitivity is good except when the number of observations and the
correlation level are small. Tuning $\alpha$ might lead to improved
selection, yet the main source of poor performance could well be the
miscalibration of the uncertainty of the predictive utility score for
misspecified models with cross-validation \citep{bengio2004no}.

@@

Figure \ref{fig:bodyfat_sensitivity_vs_fdr} shows the sensitivity
against the false discovery rate.  In almost all of the bootstrapped
subsamples, the reference
model improves the selection both in terms of sensitivity and false
discovery rate. When $n=50$, we observe worse false
discovery rates, yet by a lower amount compared to the gain in
sensitivity. Again, we observe that the benefits are more evident as
the selection becomes more challenging (i.e., lower number of
observations).
The great performance of projpred in minimal subset selection is not
carried over for the complete variable selection with iterative
projpred (even changing the reference model with a full encompassing 
linear regression with regularised horseshoe prior), and the methods 
specifically designed for the complete variable selection perform better. 
Figure \ref{fig:bodyfat_stability} shows the stability
results using the measure by
\cite{paper:stability}. The benefits of the reference model are here
marginal with only small improvements.

>>>>

In the experiments in the next Sections we include a method which we refer to as iterative lasso. It consists in the same algorithm of the iterative projection, expect for not using any reference model. Given the implementation of projpred in the R-package, it means that the predictions of the reference model consist simply on the observed target values. Iterative lasso is therefore used as the free-reference-model comparison baseline of the iterative projection.

@@

Figure \ref{fig:sensitivity_vs_fdr_iterated} shows the average sensitivity on
the vertical axis and the average false discovery rate on the
horizontal axis based on 100 data simulations for the different
combinations of $n$ and $\rho$. The best selection performance is on the
top-left corner of each plot, as it implies the lowest false discovery
rate and the highest sensitivity. We see that regardless of the
applied selection method, the use of a reference model improves the
selection performance, as it reduces the false discovery rate (shifting
to the left) or increases the sensitivity (shifting upwards). In
accordance with what can be expected, the larger data set size ($n$) and the higher the true correlations ($\rho$), the easier the
selection is. Thus, for easier selection scenarios, the benefits of
the reference model are smaller since the raw data already provide
enough information to identify the relevant variables. The iterative
projpred has good false discovery rate in all cases, and the
sensitivity is good except when the number of observations and the
correlation level are small. It performs better than the iterative lasso 
selection in any of the simulated scenarios. Tuning $\alpha$ might lead to improved
selection, yet the main source of poor performance could well be the
miscalibration of the uncertainty of the predictive utility score for
misspecified models with cross-validation \citep{bengio2004no}.

@@

Figure \ref{fig:bodyfat_sensitivity_vs_fdr} shows the sensitivity
against the false discovery rate.  In almost all of the bootstrapped
subsamples, the reference
model improves the selection both in terms of sensitivity and false
discovery rate. When $n=50$, we observe worse false
discovery rates, yet by a lower amount compared to the gain in
sensitivity. Again, we observe that the benefits are more evident as
the selection becomes more challenging (i.e., lower number of
observations).
The great performance of projpred in minimal subset selection is not
carried over for the complete variable selection with iterative
projpred (even changing the reference model with a full encompassing 
linear regression with regularised horseshoe prior), and the methods 
specifically designed for the complete variable selection perform better. 
However we still observe a better selection with respect to iterative lasso
in any of the examined scenarios, mainly in terms of false discovery rate.
Figure \ref{fig:bodyfat_stability} shows the stability
results using the measure by
\cite{paper:stability}. The benefits of the reference model are here
marginal with only small improvements.
